ms2

### 2017-10-06 ms1/ms1_display.Rmd
lots of updates

@@

@@

```{r pre_approp_table}

```

@@

```{r pde_approp_trends}

```

## Trends in diagnoses

Are some diagnoses becoming more or less common?

First, unadjusted trends in the number of diagnoses per 1,000 beneficiaries in each year. The percent change is between 2011 and 2014.

Second, adjusted trends, using Poisson regressions. The unit of analysis is the beneficiary in a year. The outcome variable is number of diagnoses in that category. The main predictor is year; the other covariates are as above. The percent change is between 2011 and 2014.

```{r dx_trends}
dx_unadj = read_tsv('tables/dx_trends_table.tsv') %>%
  #filter(year %in% c(2011, 2014)) %>%
  left_join(select(totals, year, n_bene), by='year') %>%
  mutate(dxpkp=1000*n_dx/n_bene) %>%
  select(dx_cat, year, dxpkp) %>%
  spread(year, dxpkp) %>%
  mutate(pct_change=(`2014`/`2011`-1)*100) %>%
  arrange(desc(`2011`)) %>%
  mutate_if(is.numeric, function(x) round(x, 2))

dx_adj = read_tsv('tables/dx_trends.tsv') %>%
  rename(dx_cat=model) %>%
  filter(term=='year') %>%
  mult_est(3) %>%
  model_ci() %>%
  select(dx_cat, adj_change=change_str, p.value)

dx_trends = full_join(dx_unadj, dx_adj, by='dx_cat')

dx_trends %>% kable
```

@@

```{r dx_to_pde}
dx_to_pde_unadj = read_tsv('tables/dx_rx_table.tsv') %>%
  filter(year %in% c(2011, 2014)) %>%
  select(dx_cat, antibiotic, year, f) %>%
  spread(year, f)

dx_to_pde_adj = read_tsv('tables/dx_rx_trends.tsv') %>%
  filter(term=='year') %>%
  mult_est(3) %>%
  mutate(ci=1.96*std.error,
         ci_low=estimate-ci,
         ci_high=estimate+ci) %>%
  select(dx_cat, antibiotic, estimate, ci_low, ci_high) %>%
  arrange(dx_cat, antibiotic)

@@

```{r}
x = dx_trends %>%
  select(dx_cat, `2011`:`2014`) %>%
  gather('year', 'value', `2011`:`2014`) %>%
  group_by(dx_cat) %>%
  summarize(value=mean(value)) %>%
  # convert to character to fit with other parts
  mutate(value=as.character(value)) %>%
  spread(dx_cat, value) %>%
  mutate(antibiotic='dx', key='mean_per_1kyr')
  # select(-p.value) %>%
  # gather('key', 'value', -dx_cat) %>%
  # spread(dx_cat, value) %>%
  # mutate(antibiotic='dx_trends')

@@

# Questions for the paper

## Lumping together diagnoses

I could lump the multiple tiers for diagnoses together. This
makes the table easier to interpret, but it doesn't make the point that
diagnosing patterns for multiple tiers for the same diagnosis genus have
similar dynamics, i.e., appropriate and inappropriate prescribing are changing
the same ways.

>>>>

The top 10 antibiotics account for most of the claims:

```{r top_10_fraction}
claims_by_abx %>%
  group_by(antibiotic) %>%
  summarize(n=sum(n)) %>%
  arrange(desc(n)) %>%
  mutate(f=n/sum(n), cumf=cumsum(f)) %>%
  head(10) %>%
  kable
```

@@

## Numbers of diagnoses

The fraction of diagnoses that have E&M HCPCS codes:

```{r hcpcs_count}
read_tsv('tables/hcpcs_count.tsv') %>%
  group_by(hcpcs_flag) %>%
  summarize(n_dx=sum(n_dx)) %>%
  mutate(f=n_dx/sum(n_dx)) %>%
  kable
```

The fraction of first-fill PDEs that have upstream:

```{r pde_with_dx_upstream}
read_tsv('tables/pde_with_dx_upstream.tsv') %>%
  group_by(has_dx, has_em_dx) %>%
  summarize(n=sum(n)) %>%
  ungroup() %>%
  mutate(f=n/sum(n), cumf=cumsum(f)) %>%
  kable
```

@@

@@

```{r pde_approp_trends}
read_tsv('tables/pde_approp_trends.tsv') %>%
  filter(term=='year') %>%
  select(antibiotic, estimate, p.value) %>%
  mutate(antibiotic=factor(antibiotic, levels=c('overall', top_abx))) %>%
  arrange(antibiotic) %>%
  kable
```

@@

```{r dx_to_pde}
dx_to_pde_unadj = read_tsv('tables/dx_to_pde_table.tsv') %>%
  filter(year %in% c(2011, 2014)) %>%
  select(dx_cat, antibiotic, year, f) %>%
  spread(year, f)

dx_to_pde_adj = read_tsv('tables/dx_to_pde_trends.tsv') %>%
  filter(term=='year') %>%
  mult_est(3) %>%
  mutate(ci=1.96*std.error,
         ci_low=estimate-ci,
         ci_high=estimate+ci) %>%
  select(dx_cat, antibiotic, estimate, ci_low, ci_high) %>%
  arrange(dx_cat, antibiotic)

@@

```{r}
x = read_tsv('tables/dx_cat_counts.tsv') %>%
  mutate(value=n_dx/n_bene*1000) %>%
  group_by(dx_cat) %>%
  summarize(value=mean(value)) %>%
  # convert to character to fit with other parts
  mutate(value=as.character(round(value))) %>%
  spread(dx_cat, value) %>%
  mutate(antibiotic='dx', key='mean_per_1kyr')

@@

### 2017-10-06 ms2/ms2_display.Rmd
lots of updates

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      pdf.options(useDingbats=FALSE),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, autodep=TRUE)
import::from(tools, md5sum)
library(forcats)
```

@@

ineq = ineq_table %>%
  group_by(year, unit_type, unit, drug_group) %>%
  summarize(mean=weighted.mean(n_claims, w=n_bene),
            fnz=sum(n_bene[n_claims > 0]) / sum(n_bene),
            mup=mean/fnz) %>%
  group_by(unit_type, unit, drug_group) %>%
  summarize_at(vars(mean, fnz,mup), mean) %>% 
  ungroup()

@@

@@

@@

```{r ecoli_quin_state}
state_cons_res_plot = function(b, d) {
  p = inner_join(
    ineq %>%
      filter(unit_type=='state', drug_group==d) %>%
      select(state=unit, mean),
    state_abg %>%
      filter(bug==b, drug_group==d) %>%
      select(state, percent_nonsusceptible),
    by='state') %>%
    left_join(regions, by='state') %>%
    ggplot(aes(x=mean, y=percent_nonsusceptible, label=state, color=region)) +
    geom_smooth(method='lm', se=F) +
    geom_smooth(method='lm', se=F, col='gray') +
    geom_point() +
    geom_text() +
    xlab(str_interp('mean ${d} claims per beneficiary')) +
    ylab(str_interp('mean percent nonsusceptible ${b} isolates')) +
    ggtitle(str_interp('${b} & ${d}, state'))

@@

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set    
import::from(tools, md5sum)
library(forcats)
BH = function(x) p.adjust(x, method='BH')
```

@@

ineq = ineq_table %>%
  group_by(year, unit_type, unit, drug_group) %>%
  summarize(mean=weighted.mean(n_claims, w=n_bene),
            fnz=sum(n_bene[n_claims > 0]) / sum(n_bene),
            mup=mean/fnz) %>%
  group_by(unit_type, unit, drug_group) %>%
  summarize_at(vars(mean, fnz, mup), mean) %>% 
  ungroup()

@@

```{r hrr_linear_fnz_table}
results %>%
  filter(model=='univariate_fnz', unit_type=='hrr', term=='fnz') %>%
  select(bug, drug_group, estimate, anova.p.value) %>%
  filter(anova.p.value < 0.05) %>%
  arrange(desc(estimate)) %>%
  kable
```

@@

```{r hrr_linear_mup_table}
results %>%
  filter(model=='univariate_mup', unit_type=='hrr', term=='mup') %>%
  select(bug, drug_group, estimate, anova.p.value) %>%
  filter(anova.p.value < 0.05) %>%
  arrange(desc(estimate)) %>%
  kable
```

@@

```{r ecoli_quin_state}
state_cons_res_plot = function(b, d) {
  p = inner_join(
    ineq %>%
      filter(unit_type=='state', drug_group==d) %>%
      select(state=unit, mean),
    state_abg %>%
      filter(bug==b, drug_group==d) %>%
      select(state, percent_nonsusceptible),
    by='state') %>%
    left_join(regions, by='state') %>%
    ggplot(aes(x=mean, y=percent_nonsusceptible, label=state, color=region)) +
    geom_smooth(method='lm', se=F) +
    geom_smooth(method='lm', se=F, col='gray') +
    geom_point() +
    #geom_text() +
    ggrepel::geom_text_repel() +
    xlab(str_interp('mean ${d} claims per beneficiary')) +
    ylab(str_interp('mean percent nonsusceptible ${b} isolates')) +
    ggtitle(str_interp('${b} & ${d}, state'))

@@

```{r pneumo_macro_minimal}
inner_join(
  ineq %>%
    filter(unit_type=='state', drug_group=='macrolide') %>%
    select(state=unit, fnz),
  state_abg %>%
    filter(bug=='S. pneumoniae', drug_group=='macrolide') %>%
    select(state, percent_nonsusceptible),
by='state') %>%
  left_join(regions, by='state') %>%
  ggplot(aes(x=fnz, y=percent_nonsusceptible, label=state, color=region)) +
  geom_smooth(method='lm', se=F, col='gray') +
  geom_point() +
  #geom_text() +
  ggrepel::geom_text_repel() +
  xlab(str_interp('fraction f of beneficiaries with a macrolide claim')) +
  ylab(str_interp('percent nonsusceptible pneumococcus isolates')) +
  theme_classic()
```
